COMPAS Race Analysis

### 2022-04-29 race-compas-analysis.Rmd

```{r py setup, include=FALSE}
library(reticulate)
```

```{python import, include= FALSE}
import matplotlib.pyplot as plt
import matplotlib.patches as patches
import numpy as np
import pandas as pd
import seaborn as sns

@@

```{python baseline set up}
from aif360.sklearn.preprocessing import ReweighingMeta, Reweighing
from sklearn.metrics import accuracy_score, confusion_matrix, plot_roc_curve, recall_score, precision_score

@@

# Pre-Processing Approach
```{python pre-processing set up}
lr = LogisticRegressionCV(solver='lbfgs')
rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
rew.fit(X_train, y_train)
y_pred_REW = rew.predict(X_test)
```

```{python pre-processing accuracy score} 
acc_REW = accuracy_score(y_test, y_pred_REW)
print(f'[Reweighting] The test accuracy of the algorithm is: {acc_REW: .2%}')
```

```{python pre-processing confusion matrix}
cf_matrix = confusion_matrix(y_test, y_pred_REW)
make_confusion_matrix(cf_matrix, "[Reweighting]")
plt.show()
```

@@

```{python post-processing calibrated equal odds set up}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta

>>>>

```{r py setup, include=FALSE}
library(reticulate)
#use_condaenv("base")
#if (grepl("dcaravela", Sys.getenv("HOME"))) {
 # use_condaenv("base")
#}

use_condaenv("anaconda3")
```

```{python import, include= FALSE}
#import matplotlib.pyplot as plt
import matplotlib.patches as patches
import numpy as np
import pandas as pd
import seaborn as sns

@@

```{python baseline set up, warning = FALSE, message = FALSE, echo = FALSE}
from aif360.sklearn.preprocessing import ReweighingMeta, Reweighing
from sklearn.metrics import accuracy_score, confusion_matrix, plot_roc_curve, recall_score, precision_score

@@

# Pre-Processing Approach
```{python pre-processing set up, warning = FALSE, message = FALSE, echo = FALSE}
lr = LogisticRegressionCV(solver='lbfgs')
rew = ReweighingMeta(estimator=lr, reweigher=Reweighing('race'))
rew.fit(X_train, y_train)
y_pred_REW = rew.predict(X_test)
```

```{python pre-processing accuracy score} 
acc_REW = accuracy_score(y_test, y_pred_REW)
print(f'[Reweighing] The test accuracy of the algorithm is: {acc_REW: .2%}')
```

```{python pre-processing confusion matrix}
cf_matrix = confusion_matrix(y_test, y_pred_REW)
make_confusion_matrix(cf_matrix, "[Reweighing]")
plt.show()
```

@@

```{python post-processing calibrated equal odds set up, warning = FALSE, message = FALSE, echo = FALSE}
from aif360.sklearn.postprocessing import CalibratedEqualizedOdds, PostProcessingMeta
